---
title: "ROC"
author: "Lyron Winderbaum"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ROC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(roc)
```

This document should provide a brief overview of how to generate and plot
receiver operating characteristic (ROC) curves and cost functions using 
the `roc` package. To do this I'll use a subset of Fisher's (Anderson's)
iris data to illustrate:

```{r}
y       = subset(iris, Species != "virginica")$Sepal.Width
classes = subset(iris, Species != "virginica")$Species == "setosa"
```

Note that `y` could be any numeric predictor for any boolean `classes`.
Often, `y` will be the output of calling `predict` on a fitted logistic 
model, for example. The example code below should be pretty self-explanatory.

## ROC Curve

```{r, fig.align='center'}
roc.df = roc(y, classes)
plot(roc.df$FPR, roc.df$TPR, type="l", xlab="FPR", ylab="TPR")
```

## Cost Function

```{r, fig.show='hold'}
roc.df$cost.1 = cost(roc.df$FPR, roc.df$TPR)
roc.df$cost.2 = cost(roc.df$FPR, roc.df$TPR, 3)
plot(roc.df$t, roc.df$cost.1, type="l")
plot(roc.df$t, roc.df$cost.2, type="l")
```

